---
title: "Homework6"
author: "Yanyu Zheng yz2690"
date: "March 5, 2016"
output: pdf_document
---
# 1. Chapter 9, problem 14 
```{r, results = "hide", message = FALSE}
pack = c("Sleuth3", "dplyr", "ggplot2", "car")
lapply(pack, library, character.only = TRUE)
```

## a

```{r}
attach(ex0914)
pairs(ex0914)
```

## b

```{r}
fit = lm(Heart ~ Bank + Walk + Talk, ex0914)
fit
```

## c

```{r}
plot(fit$fitted.values,fit$residuals)
```

## The variance of residuals seem to be constant throughout all levels of the fitted value. And no evidence for outliers was found.

## d

```{r}
summary(fit)
detach(ex0914)
```

# 2. Chapter 9, problem 16 

## a

```{r}
attach(ex0327)
scatterplot(PollenRemoved ~ DurationOfVisit | BeeType, ex0327, smoother = FALSE, reg.line = FALSE)
```

## No. It does not appear to be a straight line.

## b

```{r}
scatterplot(logit(PollenRemoved) ~ DurationOfVisit | BeeType, ex0327, smoother = FALSE, reg.line = FALSE)
```

## c

```{r}
scatterplot(logit(PollenRemoved) ~ log(DurationOfVisit) | BeeType, ex0327, smoother = FALSE, reg.line = FALSE)
```

## Logit VS Log seems most resonable to persuit.

## d

```{r}
fit2 = lm(logit(PollenRemoved) ~ log(DurationOfVisit) + BeeType + DurationOfVisit*BeeType)
summary(fit2)
```

## The pValue is 0.73, wchich means there's no evidence indicating the proportion of pollen depends on duration of visit differently for queens than for workers.

## e

```{r}
fit2e = lm(logit(PollenRemoved) ~ log(DurationOfVisit) + BeeType)
summary(fit2e)
detach(ex0327)
```

## Yes, queens tend to remove a smaller proportion. The cross term has high correlation with the BeeType variable, making the model highly unstable. So the diffrence in pVlue is not surprising when removing the cross term.

# 3. Chapter 9, problem 18 

## a

```{r}
attach(ex0918)
library("ggplot2")
Wings = c(Females, Males)
data3 = data.frame(Continent = as.factor(c(Continent, Continent)), Latitude = c(Latitude, Latitude), Wings = Wings, Sex = as.factor(rep(c(0,1),each = length(Continent))))
ggplot(data3, aes(x = Latitude, y = Wings, colour = Continent, shape = Sex)) + geom_point(aes(size = 3))
```
## Yes. There's no significant difference between the data from NA and EU

## b

```{r}
fit3 = lm(Wings ~ Latitude + Continent + Sex + Continent*Sex, data3)
fit3
detach(ex0918)
```

# 4. Chapter 9, problem 20 

```{r}
attach(ex0920)
plot(Year, Time)
fit41 = lm(Time~Year)
fit42 = lm(Time~Year + I(Year^2))
abline(fit41)
lines(Year,predict(fit42))
plot(Year, Speed)
fit43 = lm(Speed~Year)
fit44 = lm(Speed~Year + I(Year^2))
abline(fit43)
lines(Year,predict(fit44))
detach(ex0920)
```

## Chooes the fit43, Speed described by quadratic curve of Year.

## b

```{r}
data4 = ex0920 %>%
  filter(Track == "Fast" | Track == "Slow")
fit4b = lm(Speed~Year + I(Year^2) + Track, data4)
fit4b
```

## Fast tracks exceeds the mean on slow tracks for a speed of 0.7848 miles per hour.

## 

# 5. Chapter 10, problem 19 
```{r}

```

# 6. Chapter 10, problem 28
```{r}

```

