---
title: "Homework9"
author: "Yanyu Zheng yz2690"
date: "April 13, 2016"
output: pdf_document
---

# 1. Chapter 20, problem 12

## a

```{r}
library("Sleuth3")
library("ggplot2")
attach(ex2012)
ggplot(ex2012, aes(x=log(CK), y=H, shape=Group)) + geom_point()
```

## Yes, we can see possible connections in the plot.

## b

```{r}
myLogit1 = glm(Group ~ CK + I(CK^2), data = ex2012, family = "binomial")
summary(myLogit1)

```

## Squared term is not significant for CK or log(CK).

## c
```{r}
myLogit2 = glm(Group ~ log(CK) + I(log(CK)^2), family = "binomial")
summary(myLogit2)
```

## I choose the first model with the original scale, since the intercept and CK is significant, while the log scale model has nothing significant.

##d

```{r}
myLogit3 = glm(Group ~ log(CK) + H, family = "binomial")
myLogit4 = glm(Group ~ 1, family = "binomial")
anova(myLogit3, myLogit4)
```

##e

```{r}
p1 = predict(myLogit3, data.frame(CK = 80, H = 85))
p2 = predict(myLogit3, data.frame(CK = 300, H = 100))
inv1 = exp(p1)/(1+exp(p1))
inv2 = exp(p2)/(1+exp(p2))
inv1/inv2
detach(ex2012)
```

# 2. Chapter 21, problem 16
```{r}
attach(ex2116)
odd = Tumor/Total
oddL = exp(odd)/(1+exp(odd))
fit = lm(oddL ~ Dose)
summary(fit)
plot(fit$residuals)
## We can see non-linearity in the plot, try log transfer and square term
fit2 = lm(oddL ~ log(Dose)+log(Dose)^2)
fit2
```

## From the model, we can see the dose and the odd is definetly related. And we do a F-test to see if the difference is really significant between group.

```{r}
fitN = lm(oddL~1)
anova(fit,fitN)
```

## Again, it is significant. 

```{r}
fitNew = lm(Dose ~ odd)
predict(fitNew, data.frame(odd=0.5))
```

## The dose causing 50% tumor rate is about 0.07634605.
