---
title: "Homework4"
author: "Yanyu Zheng yz2690"
date: "February 18, 2016"
output: pdf_document
---

# 1. Chapter 5, problem 23 

```{r}
library("Sleuth3")
attach(ex0523)
anova(lm(Oxygen ~ Bone, ex0523))
```

The pValue is 9.73e-07, which means there's evidence that the means are dif- ferent for the different bones.

# 2. Chapter 5, problem 25 

```{r}
attach(ex0525)
anova(lm(log(Income2005) ~ Educ, ex0525))
```

The pValue is less than 2.2e-16 for log scale, which means the evidence is very strong for the diffenrece in income in different groups.

```{r}
## 12   13-15    16    >16
t.test(ex0525[Educ=="12","Income2005"],ex0525[Educ=="13-15","Income2005"],alternative = "less")
t.test(ex0525[Educ=="13-15","Income2005"],ex0525[Educ=="16","Income2005"],alternative = "less")
t.test(ex0525[Educ=="16","Income2005"],ex0525[Educ==">16","Income2005"],alternative = "less")
```
12 & 13-15  5346.347                
13-15 & 16  19426.6                   
16 & >16    798.1295                                 

# 3. Chapter 6, problem 12 

```{r}
attach(case0601)
library("dplyr")
data3 = case0601 %>% 
  filter(Handicap!="None") %>%
  group_by(Handicap) %>%
  summarise(mean = mean(Score),sd = sd(Score),n=n())
attach(data3)
coef = c(1/3,1/3,-1,1/3)
g = sum(coef*mean)
pooled = sqrt(sum(sd^2*(n-1))/sum(n-1))
SE = pooled*sqrt(sum(coef^2/n))
tStatistic = g/SE
## Planned comparison
pValue = 1-pt(tStatistic,52)
## Unplanned comparison
qTukey = qtukey(0.95,4,52)/sqrt(2)
```
Test statistic is `r tStatistic`. The pValue for the planned test is `r pValue`. The threshold for Tukey-Kramer test is `r qTukey`, which is larger than our test Statistic. So pValue > 0.05. 

# 4. Chapter 6, problem 15 

* a

```{r}
mean = c(30.20,28.80,26.20,31.10,30.20)
sd = c(3.82,5.26,4.66,4.91,3.53)
n = rep(9,5)
pooled = sqrt(sum((n-1)*sd^2)/sum(n-1))
```
The pooled estimate of the standard deviation is `r pooled`

*b

-1/3, 1/2, 1/2,-1/3, -1/3

*c

```{r}
coeff = c(1/3, -1/2, -1/2, 1/3, 1/3)
g = sum(coeff * mean)
sdG = pooled*sqrt(sum(coeff^2/n))
tStatistic = g/sdG
q = qt(0.975,40)
CI = c(g-sdG*q, g+sdG*q)
```
tStatistic is `r tStatistic`, qt(0.975,40) is `r q`, 95% confidence interval is `r CI`

# 5. Chapter 6, problem 16 
```{r}
LSD = qt(0.975,30)
# F value is large, no need for protected LSD
protectedLSD = qt(0.975,30)
tukey = qtukey(0.95,6,30)/sqrt(2)
bonferroni = qt(1-0.05/30,30)
sheffe = sqrt(5*qf(0.95,5,30))
```
LSD : `r LSD`                    
protectedLSD : `r protectedLSD`                         
tukey : `r tukey`                                             
bonferroni : `r bonferroni`                               
sheffe : `r sheffe`                                    

# 6. Chapter 6, problem 23

```{r}
attach(ex1420)
TukeyHSD(aov(WtLoss24~Diet, ex1420))
```
From the result, we can see that the low-fat and the low-carbohydrate group is significantly different. 95% CI is (-4.224771,-0.1408361)
