---
title: "Homework8"
author: "Yanyu Zheng yz2690"
date: "April 6, 2016"
output: pdf_document
---

# 1. Chapter 12, problem 17

## a

```{r}
library("Sleuth3")
library(leaps)
library("dplyr")
data("ex1217")

fit11 = regsubsets(Mortality~.,data=ex1217[,2:14],nvmax=13,nbest=1)
cp = summary(fit11)$cp
BIC = summary(fit11)$bic
plot(cp)
plot(BIC)
k = which.min(cp)
coef = names(coef(fit11,k)[-1])
coef = c("Mortality",coef)
data11 = ex1217[,coef]
fit11 = lm(Mortality~.,data11)
coef = c(coef,"HC","NOX","SO2")
data12 = ex1217[,coef]
data12 = mutate(data12,HC = log(HC),NOX = log(NOX), SO2 = log(SO2))
fit12 = lm(Mortality~.,data12)
anova(fit11,fit12)
```

## The p value is 0.008313

## b

```{r}
fit11 = regsubsets(Mortality~.,data=ex1217[,2:14],nvmax=13,nbest=1,method = "forward")
cp = summary(fit11)$cp
BIC = summary(fit11)$bic
plot(cp)
plot(BIC)
k = which.min(cp)
coef = names(coef(fit11,k)[-1])
coef = c("Mortality",coef)
data11 = ex1217[,coef]
fit11 = lm(Mortality~.,data11)
coef = c(coef,"HC","NOX","SO2")
data12 = ex1217[,coef]
data12 = mutate(data12,HC = log(HC),NOX = log(NOX), SO2 = log(SO2))
fit12 = lm(Mortality~.,data12)
anova(fit11,fit12)
```

## The p value is 0.008162, which is almost the same.

# 2. Chapter 12, problem 20
```{r}
data(ex1220)
data = select(ex1220,-Island,-Native)
fit21 = regsubsets(Total~.,data,nvmax=7,nbest=1,force.in = "Area")
k = which.min(summary(fit21)$cp)
coef = names(coef(fit21,k)[-1])
```

## For the total number of species, the variable selected were "Area"     "Elev"     "DistSc"   "AreaNear".

```{r}
data = select(ex1220,-Island,-Total)
fit21 = regsubsets(Native~.,data,nvmax=7,nbest=1,force.in = "Area")
k = which.min(summary(fit21)$cp)
coef = names(coef(fit21,k)[-1])
```

## For the natives, the variable selected were "Area"     "Elev"     "DistSc"   "AreaNear".

```{r}
data = ex1220 %>%
   mutate(Native = Total-Native)%>%
   select(-Island,-Total) 
fit21 = regsubsets(Native~.,data,nvmax=7,nbest=1,force.in = "Area")
k = which.min(summary(fit21)$cp)
coef = names(coef(fit21,k)[-1])
```

## For the non-natives, the variable selected were "Area"     "Elev"     "AreaNear".

# 3. Chapter 20, problem 11

## a

```{r}
data(ex2011)
logit <- glm(Failure ~ Temperature, ex2011,family = "binomial")
summary(logit)
```

## Intercept: 10.87535   sd: 5.70291
## Temperature: -0.17132   sd: 0.08344

## b
```{r}
pnorm(-2.053)
```

## The one sided p value is 0.02. 

## c
```{r}
anova(logit,test="LRT")
```

## The p value is 0.01477. 

## d
```{r}
confint.default(logit)
```

## Confidence interval for Temperature is (-0.3348573, -0.007783746)

## e
```{r}
prob = predict.glm(logit, data.frame(Temperature = 31), type="response")
problogit = predict.glm(logit, data.frame(Temperature = 31))
```

## The logit of the probability is 5.564414. The prediction of the probability of failure is 0.9961828.

## f
## Because the standard deviation of the estimate is positively related to the squared distance of the new obs and X bar. So a new obs out of the range of the exsisting Xs would lead to a prediction with high variance. 

# 4. Chapter 20, problem 15

## a
```{r}
attach(ex2015)
p = vector()
for(i in 1:7){
  p = c(p,t.test(ex2015[1:30,i+1],ex2015[31:60,i+1],alternative="less")$p.value)
}
```

## For ring 1 to 7 the p value is $`r p`$ .

## b
```{r}
logit = glm(Site~.,ex2015,family = "binomial")
summary(logit)
```

## As we can see, only ring2 and ring3 are significant, which means within 1.4km radius.
