---
title: "Homework 7"
author: "Yanyu Zheng yz2690"
date: "March 27, 2016"
output: pdf_document
---

# 3. Chapter 10, problem 26
```{r}
library("Sleuth3")
attach(ex1026)
fit11 = lm(Inhibit ~ UVB + Surface + UVB:Surface)
summary(fit11)
```

## From the summary, we can see only UVB and UVB*Surface are significant. So we build a new model with only this two variables.

```{r}
fit12 = lm(Inhibit ~ 0 + UVB + UVB:Surface)
summary(fit12)
detach(ex1026)
```

## Yes, the effect is different. The difference is about 939.931, which means the UVB change for 1, the change in Inhibit is 911.7 higher in surface than in deep sea. 

# 4. Chapter 11, problem 8

## A case with large leverage has a residual with low variability. Because its explana- tory variable values are so unusual, it dictates the location of the estimated regression over the whole region in its vicinity; no other points in the region share the responsibility. Because its residual must be small, this case acts like a mag- net on the estimated regression surface. If, however, its response falls close to the regression surface (as determined by the remaining observations alone), it is not necessarily influential. Therefore, while a large leverage does not necessarily indi- cate that the case is influential, it does imply that the case has a high potential for influence.

## plot for (b)
```{r}
set.seed(7)
x = c(1:9, 20)
y = x + rnorm(10, sd = 2)
par(mfrow=c(1,2))
plot(x,y)
fit41 = lm(y~x)
abline(fit41)
lev = hat(model.matrix(fit41))
plot(lev)
```

## From the plot we can see the last observation has high leverage but no substantial influence on the model.

## Plot for (c)

```{r}
set.seed(7)
x = c(1:9, 20)
y = x + rnorm(10, sd = 2)
y[10] = 0
par(mfrow=c(1,2))
plot(x,y)
fit42 = lm(y~x)
abline(fit42)
lev = hat(model.matrix(fit42))
plot(lev)
```

## From the plot we can see the last observation has high leverage and completely changed the model.

# 5. Chapter 11, problem 16  
```{r}
attach(case1101)
fit5 = lm(Metabol ~ Sex * Gastric)
lev = hat(model.matrix(fit5))
stud = rstudent(fit5)
cook = cooks.distance(fit5)
detach(case1101)
```

## For case 32, the leverage is `r lev[32]`, studentized residual is `r stud[32]`, cook's distance is `r cook[32]`

# 6. Chapter 11, problem 20

## a

```{r}
attach(ex1120)
fit61 = lm(Calcite ~ Carbonate)
data6 = ex1120[-which.min(Carbonate),]
fit62 = lm(Calcite ~ Carbonate, data = data6)
data6 = data6[-which.min(data6$Carbonate),]
fit63 = lm(Calcite ~ Carbonate, data = data6)
```

## Model with all obs

```{r}
summary(fit61)
```

## Model delete the smallest X

```{r}
summary(fit62)
```

## Model delete the smallest two X

```{r}
summary(fit63)
```

## b

```{r}
par(mfrow=c(1,1))
plot(Carbonate, Calcite)
abline(fit61)
abline(fit62)
abline(fit63)
```

## From the plot, we can see the points deleted have substantial influence on the regression line. Thus the change in R squared.

## c
```{r}
lev = hat(model.matrix(fit61))
plot(lev)
```

## From the plot, we can see the two smallest X have high leverage 0.56 and 0.25.

## d
```{r}
lev = hat(model.matrix(fit62))
plot(lev)
```

